---
title: "Final Project"
author: "Sabrina Hidalgo"
date: "12/9/2021"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r train}
library(tidyverse)
```

```{r, warning=FALSE,message=FALSE}
library(tidyverse)

load("FinalData.RData")
```

#I found this data on Kaggle which list the different sectors of Data Scientist (Job Title) in each state with an income level.

#I was wanting to try to predict the Sector of Accounting for Data Scientist in each State. 


#I do not know how to pull the data. 

library(caret)
set.seed(1)
trainIndex <- createDataPartition(DataScientist$Sector, p = .7, list = FALSE, times = 1)
DataScientistTrain <- DataScientist[ trainIndex,]
DataScientistValid <- DataScientist[-trainIndex,]


ggplot(data=DataScientistTrain)+geom_point(mapping = aes(x=Location,y=Job Title,color=Sector),alpha=0.5) + labs(color = "Sector")+
geom_point(data=DataScientistValid, ,mapping = aes(x=Location,y=Job Title,shape=Sector)) + labs(shape = "Testing Sector") +
  ggtitle("The data")+
  theme(plot.title = element_text(hjust=0.5, size=10, face='bold'))











