---
title: "In Class Work"
author: "Sabrina Hidalgo"
date: "9/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, warning=FALSE,message=FALSE}
library(tidyverse)

library(DBI)
db = dbConnect(RSQLite::SQLite(), dbname = "C:/Users/customer/Desktop/ACC 8143/Data Manipulation/data/03-Data-file-classroom-exercise-Chinook_Sqlite.sqlite")
               
```

```{r, echo=FALSE}

Customer<-dbReadTable(db,"Customer")

Invoice<-dbReadTable(db,"Invoice")
```

# Exercise 1

1.Using the customer table, if you select the first 5 rows what is the country in the last row? 

**Answer: Czech Republic**

```{r echo=TRUE}

head(Customer,5)

knitr::kable(head(Customer,5), caption = "The resulting data")%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%", height = "300px")

```


2.Filter the Invoice data set using the BillingCountry column. Your results should only have 3 countries of your choice.

**Answer: USA, ITALY, BRAZIL**

```{r echo=TRUE}

filter3countries<-Invoice%>%
  filter(BillingCountry %in% c("USA","Italy","Brazil"))

head(filter3countries,5)

knitr::kable(filter3countries, caption = "The resulting data")%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%", height = "300px")

```


3.Filter the Invoice data set such that the results do NOT contain 2 countries of your choice.

**Answer: Does not include USA and Germany**
```{r echo=TRUE}
drop2Countries<-Invoice%>%
  filter(!(BillingCountry=="USA" | BillingCountry=="Germany"))

knitr::kable(drop2Countries, caption = "The resulting data")%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%", height = "300px")
```

4.Filter the Invoice data set such that the results only have invoices with totals over 10.00.

**Answer: In table below**
```{r}

Totover10<-Invoice%>%
  filter(Total>10)

knitr::kable(Totover10, caption = "The resulting data")%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%", height = "300px")


```


## Exercise 2
1.What is the mean invoice total for the USA?

**MEAN TOTAL = 5.747912**
```{r}
summary_invoice<-Invoice%>%
  group_by(BillingCountry=="USA")%>%
  summarise(mean_Total=mean(Total,na.rm=TRUE))

summary_invoice 

knitr::kable ((Invoice), caption = "The resulting data")%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%", height = "300px")


```

2.What is the mean invoice total for the USA by State?
**Answer: In table**

```{r}
summary_invoice<-Invoice%>%
  filter(BillingCountry=="USA")%>%
  group_by(BillingState)%>%
 
 summarise(mean_Total=mean(Total,na.rm=TRUE))

knitr::kable(summary_invoice)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")



```

3.What is the mean invoice total for the USA by State and City?
**Answer= In Table**
```{r}
summary_invoice<-Invoice%>%
  filter(BillingCountry=="USA")%>%
  group_by(BillingState, BillingCity)%>%
 
 summarise(mean_Total=mean(Total,na.rm=TRUE))
knitr::kable(summary_invoice)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")

```

4. What is the mean invoice total and number of invoices for the USA by State and City?
**Answer= In Table**

```{r}
summary_invoice<-Invoice%>%
  filter(BillingCountry=="USA")%>%
  group_by(BillingState, BillingCity)%>%
 
 summarise(mean_Total=mean(Total,na.rm=TRUE),
           numberofinvoices=n())

knitr::kable(summary_invoice)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")

```
```{r}
library(curl)

load(curl("https://raw.githubusercontent.com/Professor-Hunt/ACC3053/main/data/AnnualCompanyData.Rda"))
```


## Exercise 3

1.With the AnnualCompanyData dataset construct a dataset that contains CompanyName, FiscalYear, CurrentAssets, TotalInventory, CurrentLiab AND the necessary variables to construct Debt ratio. Using mutate construct AcidTest_Ratio, Current_Ratio, and Debt_Ratio.

```{r}
DebtTest_Ratio<-AnnualCompanyData%>%
  select(CompanyName,FiscalYear,CurrentAssets,TotalInventory,CurrentLiab,CurrentDebt,LongtermDebt,TotalAssets)%>%
  mutate(DebtTest_Ratio=(CurrentDebt+LongtermDebt)/TotalAssets,Current_Ratio=CurrentAssets/CurrentLiab,AcidTest_Ratio=(CurrentAssets-TotalInventory)/CurrentLiab )
  
knitr::kable(DebtTest_Ratio)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")

```


2.Using the dataset in the previous question. Compute the summary statistics for Debt_Ratio and discuss what the summary stats tell you.

**Answer: Out of the column of DebtTest_Ratio, it is pulling the numbers for each category. For instance, 0 must be the min number in the column. The mean is .277 out of the column.**

```{r}
DebtTest_Summary <- DebtTest_Ratio %>% 
  summarize(
    min = min(DebtTest_Ratio, na.rm = TRUE),
    q1 = quantile(DebtTest_Ratio, 0.25, na.rm = TRUE),
    median = quantile(DebtTest_Ratio, 0.5, na.rm = TRUE),
    q3 = quantile(DebtTest_Ratio, 0.75, na.rm = TRUE),
    max = max(DebtTest_Ratio, na.rm = TRUE),
    mean = mean(DebtTest_Ratio, na.rm = TRUE),
    sd = sd(DebtTest_Ratio, na.rm = TRUE),
    missing = sum(is.na(DebtTest_Ratio))
  )

knitr::kable(DebtTest_Summary)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")


```

3. With your explanation from question 2, arrange your data based on Debt_Ratio explain why you see the certain companies with high/low debt ratio.


```{r}

Arranged_Debt<-DebtTest_Ratio%>%
  arrange(DebtTest_Ratio)

knitr::kable(Arranged_Debt)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")

```

4.Arrange the data based on Debt_Ratio and AcidTest_Ratio (ascending) and pick a company in the top 20 and explain why they appear there.
```{r}
Multple_Arrange<-AnnualCompanyData%>%
      select(CompanyName,FiscalYear,CurrentAssets,TotalInventory,CurrentLiab,CurrentDebt,LongtermDebt,TotalAssets)%>%
      mutate(AcidTest_Ratio=(CurrentAssets-TotalInventory)/CurrentLiab,DebtTest_Ratio=(CurrentDebt+LongtermDebt)/TotalAssets)%>%
      arrange(desc(AcidTest_Ratio,Debt_Ratio))

knitr::kable(Multple_Arrange)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")


```

## Exercise 4

```{r}
Track<-dbReadTable(db, "Track")

Album<-dbReadTable(db, "Album")

Genre<-dbReadTable(db, "Genre")

InvoiceLine<-dbReadTable(db, "InvoiceLine")
```

1.Return the top five most downloaded tracks with the full name of the track and number of downloads.
```{r}
top5DL<-Track%>%
  inner_join(InvoiceLine, by="TrackId")%>%
  group_by(TrackId)%>%
  mutate(Downloads=sum(Quantity, na.rm = TRUE))%>%
  select(TrackId,Name,Downloads)%>%
  distinct(TrackId, .keep_all = TRUE)%>%
  arrange(desc(Downloads))

knitr::kable(top5DL)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")

```

2. How many distinct albums have actually been downloaded? Hint we need the Album table.

*Answer: 304*

```{r}
Albums_Downloaded<-InvoiceLine%>%
  inner_join(Track, by="TrackId")%>%
  inner_join(Album, by="AlbumId")%>%
  distinct(AlbumId)%>%
  summarise(Number_Albums_Downloaded=n())

knitr::kable(Albums_Downloaded)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")


```

3. What is the most popular genre? Hint you need the Genre table.
**Answer: Rock**
```{r}

Genre_Pop<-InvoiceLine%>%
  inner_join(Track, by="TrackId")%>%
  group_by(GenreId)%>%
  summarise(Genre_Downloaded=n())%>%
 inner_join(Genre, by="GenreId")%>%
  arrange(desc(Genre_Downloaded))

knitr::kable(Genre_Pop)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "100%",height="300px")
```






